---
title: "Behavioral Journey Map Analysis - Complete Decision Tool (V2)"
author: "George Wanjiru"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    code_folding: show
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```
###Installing Core Libraries
```{r}
# Core libraries
required_packages <- c(
  "tidyverse", "visNetwork", "shiny", "shinyWidgets", "DT",
  "igraph", "RColorBrewer", "scales", "shinythemes", "plotly",
  "htmltools", "randomForest", "cluster", "readxl", "openxlsx"
)

installed <- rownames(installed.packages())
missing_packages <- setdiff(required_packages, installed)
if (length(missing_packages) > 0) {
}
lapply(required_packages, library, character.only = TRUE)
```
###Loading Data 
```{r}
load_all_data <- function() {
  cat("Please select the main mapping matrix CSV file...\n")
  main_matrix <- read.csv(file.choose(), stringsAsFactors = FALSE)
  # Let R auto-convert names with make.names
  colnames(main_matrix) <- make.names(colnames(main_matrix))
  main_matrix[is.na(main_matrix)] <- ""
  main_matrix <- main_matrix %>% distinct()
  
  cat("Please select the glossary CSV file...\n")
  glossary_raw <- read.csv(file.choose(), header = FALSE, stringsAsFactors = FALSE)
  
  cat("Please select the behavior network CSV file (press Cancel to skip)...\n")
  behavior_network <- tryCatch({
    read.csv(file.choose(), stringsAsFactors = FALSE)
  }, error = function(e) {
    message("No behavior network file selected.")
    return(NULL)
  })
  
  return(list(matrix = main_matrix, glossary_raw = glossary_raw, behavior_network = behavior_network))
}

data_loaded <- load_all_data()
main_matrix <- data_loaded$matrix
glossary_raw <- data_loaded$glossary_raw
behavior_network_raw <- data_loaded$behavior_network

cat("\n=== DATA LOADED ===\n")
cat("Main matrix:", nrow(main_matrix), "rows,", ncol(main_matrix), "columns\n")
cat("Column names:\n", paste(colnames(main_matrix), collapse = "\n  "), "\n")
if(!is.null(behavior_network_raw)) {
  cat("Behavior network:", nrow(behavior_network_raw), "rows loaded\n")
}
```

###Set Column Names to Detect Dynamically
```{r}
# ============================================
# DETECT ACTUAL COLUMN NAMES DYNAMICALLY
# ============================================

# Print all columns to help debug
cat("\n=== ALL COLUMNS IN MAIN MATRIX ===\n")
for(i in 1:ncol(main_matrix)) {
  cat(sprintf("%2d: [%s]\n", i, colnames(main_matrix)[i]))
}

# Helper to find column by keyword
find_col <- function(keywords) {
  for(kw in keywords) {
    matches <- grep(kw, colnames(main_matrix), ignore.case = TRUE, value = TRUE)
    if(length(matches) > 0) return(matches[1])
  }
  return(NULL)
}

# Map ALL columns we need
col_journey    <- find_col(c("Journey"))
col_actor      <- find_col(c("Actor"))
col_cause      <- find_col(c("Cause"))
col_desc       <- find_col(c("Description", "Notes"))
col_infl_notes <- find_col(c("Not in the map"))
col_infl1      <- find_col(c("Influence.*Theme.*Level.1", "Influence Theme.*1"))
col_infl2      <- find_col(c("Influence.*Theme.*Level.2", "Influence Theme.*2"))
col_infl3      <- find_col(c("Influence.*Theme.*Level.3", "Influence Theme.*3"))
col_eff1       <- find_col(c("Effect.*Theme.*Level.1", "Effect Theme.*1"))
col_eff2       <- find_col(c("Effect.*Theme.*Level.2", "Effect Theme.*2"))
col_eff_cat    <- find_col(c("Effect.*Category", "Behavior.*Influence"))
col_eff_actor  <- find_col(c("Effect.*Actor"))
col_count      <- find_col(c("Count"))
col_effect_dir <- find_col(c("Effect of the influence", "Negative.*Positive.*Mixed"))
col_comb       <- find_col(c("COM.B", "COM-B"))
col_sem        <- find_col(c("SEM"))
col_subsystem  <- find_col(c("Sub.system", "Sub-system"))

# Print what we found
cat("\n=== DETECTED COLUMN MAPPINGS ===\n")
mappings <- list(
  "Journey" = col_journey, "Actor" = col_actor, "Cause" = col_cause,
  "Description" = col_desc, "L1 Influence" = col_infl1,
  "L2 Influence Theme" = col_infl2, "L3 Influence" = col_infl3,
  "L2 Behavior (Effect)" = col_eff2, "Effect Actor" = col_eff_actor,
  "Count" = col_count, "Effect Direction" = col_effect_dir,
  "COM-B" = col_comb, "SEM Level" = col_sem
)
for(name in names(mappings)) {
  cat(sprintf("  %-25s = %s\n", paste0(name, ":"), 
              ifelse(is.null(mappings[[name]]), "❌ NOT FOUND", mappings[[name]])))
}

# Check critical columns
critical <- c("col_journey", "col_actor", "col_infl3", "col_eff2")
missing_crit <- critical[sapply(critical, function(x) is.null(get(x)))]
if(length(missing_crit) > 0) {
  stop("CRITICAL: Cannot find columns: ", paste(missing_crit, collapse = ", "),
       "\nCheck the column names printed above.")
}
```

###Data Quality Checks and Cleaning
```{r}
# ============================================
# DATA QUALITY CHECKS & CLEANING
# ============================================

# Clean actor names
clean_actor_names <- function(actor_vec) {
  actor_vec <- str_trim(actor_vec)
  actor_vec <- gsub("\\s+", " ", actor_vec)
  actor_vec <- case_when(
    grepl("^Citizen", actor_vec, ignore.case = TRUE) ~ "Citizen",
    grepl("^CSO|Civil Society", actor_vec, ignore.case = TRUE) ~ "CSO",
    grepl("^Policy|Policymaker", actor_vec, ignore.case = TRUE) ~ "Policy maker",
    grepl("^Local|Local Govt", actor_vec, ignore.case = TRUE) ~ "Local Govt official",
    grepl("^Religious", actor_vec, ignore.case = TRUE) ~ "Religious leader",
    grepl("^Media professional|Media professsional", actor_vec, ignore.case = TRUE) ~ "Media professional",
    grepl("^Social media", actor_vec, ignore.case = TRUE) ~ "Social media",
    grepl("^Government|^Govt", actor_vec, ignore.case = TRUE) ~ "Government Official",
    grepl("^Women", actor_vec, ignore.case = TRUE) ~ "Women",
    TRUE ~ actor_vec
  )
  return(actor_vec)
}

# Apply actor cleaning
main_matrix[[col_actor]] <- clean_actor_names(main_matrix[[col_actor]])
if(!is.null(col_eff_actor)) {
  main_matrix[[col_eff_actor]] <- clean_actor_names(main_matrix[[col_eff_actor]])
}

cat("\n=== ACTORS CLEANED ===\n")
all_actors <- unique(c(main_matrix[[col_actor]], main_matrix[[col_eff_actor]]))
cat("Unique actors:", length(all_actors), "\n")
cat(paste("  -", sort(all_actors), collapse = "\n"), "\n")

# Check effect direction values
cat("\n=== EFFECT DIRECTION VALUES ===\n")
if(!is.null(col_effect_dir)) {
  effect_raw <- main_matrix[[col_effect_dir]]
  cat("Sample values:", paste(head(unique(effect_raw), 10), collapse = ", "), "\n")
}

# Create quality check export
quality_check_table <- main_matrix %>%
  select(
    Journey = all_of(col_journey),
    Actor = all_of(col_actor),
    L3_Influence = all_of(col_infl3),
    L2_Behavior = all_of(col_eff2),
    Effect_Actor = all_of(col_eff_actor),
    Effect_Direction = if(!is.null(col_effect_dir)) all_of(col_effect_dir) else all_of(col_journey),
    Count = if(!is.null(col_count)) all_of(col_count) else all_of(col_journey),
    COM_B = if(!is.null(col_comb)) all_of(col_comb) else all_of(col_journey)
  ) %>%
  distinct()

# If we accidentally selected journey multiple times, fix
if(!is.null(col_effect_dir) && !is.null(col_count) && !is.null(col_comb)) {
  # Good, all columns exist
} else {
  # Fix the table for export
  quality_check_table <- main_matrix %>%
    select(
      Journey = all_of(col_journey),
      Actor = all_of(col_actor),
      L3_Influence = all_of(col_infl3),
      L2_Behavior = all_of(col_eff2)
    ) %>%
    distinct()
}

# Export
output_dir <- getwd()
quality_check_file <- file.path(output_dir, paste0("data_quality_check_", Sys.Date(), ".xlsx"))

tryCatch({
  write.xlsx(list(
    "Unique_Pairings" = quality_check_table,
    "Unique_Actors" = data.frame(Actor = sort(all_actors)),
    "Column_Mapping" = data.frame(
      Purpose = names(mappings),
      Detected_Column = unlist(lapply(mappings, function(x) ifelse(is.null(x), "NOT FOUND", x)))
    )
  ), quality_check_file)
  cat("\n✅ Quality check file saved:", quality_check_file, "\n")
}, error = function(e) {
  cat("\n⚠️ Could not save quality check file:", e$message, "\n")
})
```

###Glossary Cleaning
```{r}
# ============================================
# GLOSSARY CLEANING
# ============================================

# STEP 1: Promote first row to column names
colnames(glossary_raw) <- as.character(unlist(glossary_raw[1, ]))

# STEP 2: Remove the header row from the data
glossary_clean <- glossary_raw[-1, ]

# Remove columns whose header is NA or blank
valid_cols <- !is.na(colnames(glossary_clean)) & trimws(colnames(glossary_clean)) != ""
glossary_clean <- glossary_clean[, valid_cols]

# STEP 3: Clean column names for safe R usage
# STEP 3: Clean and make column names unique
raw_names <- as.character(colnames(glossary_clean))
raw_names[is.na(raw_names) | trimws(raw_names) == ""] <- "empty_col"
colnames(glossary_clean) <- make.unique(make.names(raw_names))
# Inspect names after cleaning
print(colnames(glossary_clean))

# STEP 4: Identify glossary term and definition columns
find_col_glossary <- function(df, keywords) {
  for (kw in keywords) {
    matches <- grep(kw, colnames(df), ignore.case = TRUE, value = TRUE)
    if (length(matches) > 0) return(matches[1])
  }
  stop(paste("Could not find column matching:", paste(keywords, collapse = ", ")))
}

name_col <- find_col_glossary(
  glossary_clean,
  c("Influence", "Behavior", "Name", "Term")
)

# Force Description column - look for exact match first
def_col <- if("Description" %in% colnames(glossary_clean)) {
  "Description"
} else {
  find_col_glossary(
    glossary_clean,
    c("Description", "Definition")
  )
}
cat("Using definition column:", def_col, "\n")

# STEP 5: Rename to standard internal names
glossary_clean <- glossary_clean %>%
  rename(
    name = all_of(name_col),
    definition = all_of(def_col)
  ) %>%
  filter(
    !is.na(name),
    name != "",
    !grepl("^\\s*$", name)
  ) %>%
  distinct(name, .keep_all = TRUE)

# Check result
glimpse(glossary_clean)

# DEBUG: Check how many definitions are non-empty
cat("\n=== GLOSSARY DIAGNOSTIC ===\n")
cat("Total rows:", nrow(glossary_clean), "\n")
cat("Non-empty definitions:", sum(!is.na(glossary_clean$definition) & glossary_clean$definition != ""), "\n")
cat("Empty definitions:", sum(is.na(glossary_clean$definition) | glossary_clean$definition == ""), "\n")
cat("Sample names:", paste(head(glossary_clean$name, 10), collapse = ", "), "\n")
cat("Sample definitions (first 3):\n")
for(i in 1:min(3, nrow(glossary_clean))) {
  cat(sprintf("  [%s]: %s\n", 
      substr(glossary_clean$name[i], 1, 40),
      substr(glossary_clean$definition[i], 1, 80)))
}

# L4 Categories to highlight
l4_categories <- c(
  "INFORMATION ACCESS AND QUALITY",
  "TRUST AND CREDIBILITY",
  "INSTITUTIONAL SYSTEMS",
  "POWER, POLITICS AND INCENTIVES",
  "CAPABILITY AND KNOWLEDGE",
  "SOCIAL NORMS AND COLLECTIVE BEHAVIOR",
  "PSYCHOLOGICAL AND EMOTIONAL DRIVERS"
)

glossary_clean <- glossary_clean %>%
  mutate(
    is_l4 = toupper(trimws(name)) %in% toupper(l4_categories),
    level = ifelse(is_l4, "L4 System Level", "L3 Influence")
  )

cat("\n=== GLOSSARY CLEANED ===\n")
cat("Terms:", nrow(glossary_clean), "\n")
cat("L4 Categories found:", sum(glossary_clean$is_l4), "\n")
cat("L4s:", paste(glossary_clean$name[glossary_clean$is_l4], collapse = ", "), "\n")
```

###Cleaning Main Data
```{r}
# ============================================
# CLEAN AND PREPARE MAIN DATA
# ============================================

# Remove empty rows
main_matrix <- main_matrix %>%
  filter(.data[[col_infl3]] != "" | .data[[col_eff2]] != "")

# Clean text
char_cols <- sapply(main_matrix, is.character)
for(cn in names(char_cols)[char_cols]) {
  main_matrix[[cn]] <- str_trim(main_matrix[[cn]])
  main_matrix[[cn]] <- gsub("\\s+", " ", main_matrix[[cn]])
}

# Convert count
if(!is.null(col_count)) {
  main_matrix$Count_numeric <- suppressWarnings(as.numeric(as.character(main_matrix[[col_count]])))
  main_matrix$Count_numeric[is.na(main_matrix$Count_numeric)] <- 1
} else {
  main_matrix$Count_numeric <- 1
}

# Convert effect direction
main_matrix$Effect_numeric <- 0
if(!is.null(col_effect_dir)) {
  raw_eff <- as.character(main_matrix[[col_effect_dir]])
  main_matrix$Effect_numeric <- suppressWarnings(as.numeric(raw_eff))
  main_matrix$Effect_numeric[is.na(main_matrix$Effect_numeric)] <- 0
  
  # CONVERT: 0 (Negative) → -1, 1 (Positive) → 1, 2 (Mixed) → 0
  cat("\nConverting effect values:\n")
  cat("  Before: 0=Negative, 1=Positive, 2=Mixed\n")
  
  main_matrix$Effect_numeric <- case_when(
    main_matrix$Effect_numeric == 0 ~ -1,   # Negative → -1
    main_matrix$Effect_numeric == 1 ~ 1,    # Positive → 1
    main_matrix$Effect_numeric == 2 ~ 0,    # Mixed → 0
    TRUE ~ main_matrix$Effect_numeric
  )
  
  cat("  After: -1=Negative, 0=Mixed, 1=Positive\n")
}
cat("\n=== JOURNEY VALUES IN DATA ===\n")
print(table(main_matrix[[col_journey]]))
```
###Building Nodes
```{r}
# ============================================
# BUILD NODES - USING L2 AS PRIMARY INFLUENCES
# ============================================
# ============================================
# VERIFY INFLUENCE VS BEHAVIOR CATEGORIES
# ============================================
cat("\n=== EFFECT CATEGORY CHECK ===\n")
if(!is.null(col_eff_cat)) {
  cat("Effect Category column:", col_eff_cat, "\n")
  cat("Values:\n")
  print(table(main_matrix[[col_eff_cat]], useNA = "ifany"))
  
  # Check which rows are influences vs behaviors based on this column
  cat("\nSample rows where Effect Category = 'Influence':\n")
  inf_rows <- main_matrix[grepl("Influence", main_matrix[[col_eff_cat]], ignore.case = TRUE), ]
  cat("Count:", nrow(inf_rows), "\n")
  if(nrow(inf_rows) > 0) {
    cat("Sample L3 values:", paste(head(inf_rows[[col_infl3]], 3), collapse = ", "), "\n")
  }
  
  cat("\nSample rows where Effect Category = 'Behavior':\n")
  beh_rows <- main_matrix[grepl("Behavior", main_matrix[[col_eff_cat]], ignore.case = TRUE), ]
  cat("Count:", nrow(beh_rows), "\n")
  if(nrow(beh_rows) > 0) {
    cat("Sample L2 values:", paste(head(beh_rows[[col_eff2]], 3), collapse = ", "), "\n")
  }
  
  # Export this check
  category_check <- data.frame(
    Effect_Category = main_matrix[[col_eff_cat]],
    L3_Influence = main_matrix[[col_infl3]],
    L2_Behavior = main_matrix[[col_eff2]],
    Journey = main_matrix[[col_journey]],
    stringsAsFactors = FALSE
  ) %>%
    group_by(Effect_Category) %>%
    summarise(
      Count = n(),
      Sample_Influences = paste(unique(head(L3_Influence, 3)), collapse = " | "),
      Sample_Behaviors = paste(unique(head(L2_Behavior, 3)), collapse = " | "),
      .groups = "drop"
    )
  
  cat("\nCategory Summary:\n")
  print(category_check)
} else {
  cat("WARNING: Effect Category column not found. Using all rows for both influences and behaviors.\n")
}
# First, check what column to use for influence vs behavior
cat("\n=== CHECKING INFLUENCE/BEHAVIOR CATEGORIES ===\n")
if(!is.null(col_eff_cat)) {
  cat("Effect Category values:\n")
  print(table(main_matrix[[col_eff_cat]]))
}

# L2 influences = main display influences
# L3 influences = system level (used as filter)
Actor_col <- main_matrix[[col_actor]]
Effect_Actor_col <- if(!is.null(col_eff_actor)) main_matrix[[col_eff_actor]] else ""
Journey_col <- main_matrix[[col_journey]]
COM_B_col <- if(!is.null(col_comb)) main_matrix[[col_comb]] else ""
SEM_col <- if(!is.null(col_sem)) main_matrix[[col_sem]] else ""
Desc_col <- if(!is.null(col_desc)) main_matrix[[col_desc]] else ""

# Use L2 as primary influence nodes (more granular)
nodes <- data.frame(
  name = c(main_matrix[[col_infl2]], main_matrix[[col_eff2]]),
  description = c(Desc_col, Desc_col),
  actor = c(Actor_col, Effect_Actor_col),
  comb = c(COM_B_col, COM_B_col),
  journey = c(Journey_col, Journey_col),
  l3_category = c(main_matrix[[col_infl3]], rep("", nrow(main_matrix))),  # L3 as filter
  sem_level = c(SEM_col, SEM_col),
  level = c(rep("L2 Influence", nrow(main_matrix)), rep("Behavior", nrow(main_matrix))),
  type = c(rep("Influence", nrow(main_matrix)), rep("Behavior", nrow(main_matrix))),
  stringsAsFactors = FALSE
) %>%
  filter(name != "", !is.na(name)) %>%
  distinct(name, type, .keep_all = TRUE)

cat("\nNodes before deduplication:", nrow(nodes), "\n")

# Calculate metrics
counts <- bind_rows(
  main_matrix %>%
    filter(.data[[col_infl2]] != "") %>%
    group_by(name = .data[[col_infl2]]) %>%
    summarise(mentions = sum(Count_numeric, na.rm = TRUE),
              avg_effect = mean(Effect_numeric, na.rm = TRUE), .groups = "drop"),
  main_matrix %>%
    filter(.data[[col_eff2]] != "") %>%
    group_by(name = .data[[col_eff2]]) %>%
    summarise(mentions = n(),
              avg_effect = mean(Effect_numeric, na.rm = TRUE), .groups = "drop")
) %>%
  group_by(name) %>%
  summarise(mentions = sum(mentions), avg_effect = mean(avg_effect), .groups = "drop")

nodes <- nodes %>%
  left_join(counts, by = "name") %>%
  mutate(
    mentions = ifelse(is.na(mentions), 1, mentions),
    avg_effect = ifelse(is.na(avg_effect), 0, avg_effect)
  )

# Add glossary
n# Check which nodes match glossary
cat("\n=== GLOSSARY MATCHING ===\n")
cat("Nodes before join:", nrow(nodes), "\n")

nodes <- nodes %>%
  left_join(
    glossary_clean %>% select(name, definition, is_l4),
    by = "name"
  )

cat("Matched definitions:", sum(!is.na(nodes$Description)), "/", nrow(nodes), "\n")
cat("Unmatched nodes:", sum(is.na(nodes$Description)), "\n")
if(sum(is.na(nodes$Description)) > 0) {
  cat("Sample unmatched:\n")
  unmatched <- nodes %>% filter(is.na(Description)) %>% pull(name) %>% unique() %>% head(10)
  cat(paste("  -", unmatched, collapse = "\n"), "\n")
}

nodes <- nodes %>%
  mutate(
    Description = case_when(
      !is.na(definition) & definition != "" ~ definition,
      !is.na(description) & description != "" ~ substr(description, 1, 200),
      TRUE ~ name
    ),
    is_l4 = ifelse(is.na(is_l4), FALSE, is_l4)
  )

cat("Final Description coverage:", sum(nodes$Description != nodes$name & nodes$Description != ""), "/", nrow(nodes), "\n")

nodes$id <- 1:nrow(nodes)
nodes$effect_type <- case_when(
  nodes$avg_effect > 0.3 ~ "Lever (Positive)",
  nodes$avg_effect < -0.3 ~ "Barrier (Negative)",
  TRUE ~ "Both/Mixed"
)

# Simple colors
nodes$color.background <- ifelse(nodes$type == "Influence", "#3498db", "#9b59b6")
nodes$color.border <- "#333333"
nodes$borderWidth <- 1
# Only highlighted gaps get red border, otherwise kept subtle
nodes$size <- scales::rescale(log(nodes$mentions + 1), to = c(15, 35))
nodes$shape <- ifelse(nodes$type == "Influence", "dot", "diamond")
nodes$font.size <- 14
nodes$font.color <- "#2C3E50"
nodes$shadow <- TRUE

cat("\nNodes built:", nrow(nodes), "\n")

# ============================================
# BUILD EDGES
# ============================================

edges <- main_matrix %>%
  filter(.data[[col_infl2]] != "", .data[[col_eff2]] != "") %>%
  transmute(
    from_name = .data[[col_infl2]],    
    to_name = .data[[col_eff2]],
    direction = Effect_numeric,
    weight = Count_numeric,
    actor_from = .data[[col_actor]],
    actor_to = if(!is.null(col_eff_actor)) .data[[col_eff_actor]] else "",
    journey = .data[[col_journey]]
  ) %>%
  group_by(from_name, to_name) %>%
  summarise(
    direction = mean(direction, na.rm = TRUE),
    weight = sum(weight, na.rm = TRUE),
    actor_from = first(actor_from),
    actor_to = first(actor_to),
    journey = first(journey),
    .groups = "drop"
  ) %>%
  mutate(weight = ifelse(is.na(weight) | weight == 0, 1, weight))

# Map to IDs
edges <- edges %>%
  left_join(nodes %>% select(id, name), by = c("from_name" = "name")) %>%
  rename(from = id) %>%
  left_join(nodes %>% select(id, name), by = c("to_name" = "name")) %>%
  rename(to = id) %>%
  filter(!is.na(from), !is.na(to))

# Map to IDs
# Check what columns we have before mapping
cat("\n=== EDGE MAPPING DEBUG ===\n")
cat("Edges columns before mapping:", paste(colnames(edges), collapse = ", "), "\n")
cat("Sample from_names:", paste(head(edges$from_name, 5), collapse = ", "), "\n")
cat("Sample to_names:", paste(head(edges$to_name, 5), collapse = ", "), "\n")

# Simple approach: map names to IDs manually
# Create lookup table from nodes
node_lookup <- nodes %>% select(id, name)
cat("Node lookup rows:", nrow(node_lookup), "\n")

# Map from_name to from ID
edges$from <- node_lookup$id[match(edges$from_name, node_lookup$name)]
edges$to <- node_lookup$id[match(edges$to_name, node_lookup$name)]

cat("Edges with from/to IDs:\n")
cat("  from IDs - NA count:", sum(is.na(edges$from)), "\n")
cat("  to IDs - NA count:", sum(is.na(edges$to)), "\n")

# Filter to only valid edges
edges <- edges %>%
  filter(!is.na(from), !is.na(to))

cat("  Valid edges after filtering:", nrow(edges), "\n")

# Remove the name columns (keep IDs)
edges <- edges %>%
  select(from, to, direction, weight, actor_from, actor_to, journey)

# ADD THESE DEBUG LINES:
cat("\n=== EDGE MATCHING DIAGNOSTIC ===\n")
cat("Total edges before ID mapping:", nrow(main_matrix %>% filter(.data[[col_infl2]] != "", .data[[col_eff2]] != "")), "\n")
cat("Edges after ID mapping:", nrow(edges), "\n")
cat("Edges lost (no node match):", 
    nrow(main_matrix %>% filter(.data[[col_infl2]] != "", .data[[col_eff2]] != "")) - nrow(edges), "\n")

if(nrow(edges) == 0) {
  cat("\n⚠️ NO EDGES MATCHED! Checking name alignment...\n")
  cat("Sample edge from_names:\n")
  print(head(unique(main_matrix[[col_infl2]][main_matrix[[col_infl2]] != ""]), 10))
  cat("\nSample node names:\n")
  print(head(nodes$name[nodes$type == "Influence"], 10))
}

# Arrow colors
# Edge colors based on converted values
cat("\n=== EDGE DIRECTION DISTRIBUTION ===\n")
cat("Negative (-1):", sum(edges$direction < 0), "\n")
cat("Neutral (0):", sum(edges$direction == 0), "\n")
cat("Positive (1):", sum(edges$direction > 0), "\n")

edges$color <- case_when(
  edges$direction > 0 ~ "#2ecc71",   # Green for positive
  edges$direction < 0 ~ "#e74c3c",   # Red for negative
  TRUE ~ "#f39c12"                    # Orange for neutral/mixed
)

cat("Edge colors assigned:", paste(names(table(edges$color)), collapse = ", "), "\n")

edges$width <- scales::rescale(log(edges$weight + 1), to = c(1, 5))
edges$arrows <- "to"
edges$smooth <- TRUE

# Ensure arrows are always enabled
edges$arrows <- list(
  to = list(enabled = TRUE, scaleFactor = 1)
)

# Print edge summary for debugging
cat("\n=== EDGES BUILT ===\n")
cat("Total edges:", nrow(edges), "\n")
cat("Edge columns:", paste(colnames(edges), collapse = ", "), "\n")
cat("Color distribution:\n")
print(table(edges$color))

edges$title <- paste0(
  "<b>", edges$actor_from, " → ", edges$actor_to, "</b><br>",
  "Effect: ", round(edges$direction, 2), "<br>",
  "Weight: ", edges$weight
)

cat("Edges built:", nrow(edges), "\n")
cat("Edge colors:", paste(names(table(edges$color)), collapse = ", "), "\n")
```
###Wrapping Glossary Definitions and creating tooltips
```{r}
wrap_text <- function(text, width = 50) {
  if (is.na(text) || is.null(text) || text == "") return("No description available")
  words <- strsplit(as.character(text), " ")[[1]]
  lines <- character()
  current_line <- ""
  for (word in words) {
    if (nchar(paste(current_line, word)) <= width) {
      current_line <- if (current_line == "") word else paste(current_line, word)
    } else {
      lines <- c(lines, current_line)
      current_line <- word
    }
  }
  lines <- c(lines, current_line)
  paste(lines, collapse = "<br>")
}

create_tooltips <- function(nodes) {
  tooltips <- character(nrow(nodes))
  for(i in 1:nrow(nodes)) {
    eff_badge <- case_when(
      nodes$effect_type[i] == "Lever (Positive)" ~ 
        '<span style="background:#2ecc71;color:white;padding:2px 8px;border-radius:10px;">Lever</span>',
      nodes$effect_type[i] == "Barrier (Negative)" ~ 
        '<span style="background:#e74c3c;color:white;padding:2px 8px;border-radius:10px;">Barrier</span>',
      TRUE ~ '<span style="background:#f39c12;color:white;padding:2px 8px;border-radius:10px;">Mixed</span>'
    )
    
    if(nodes$type[i] == "Influence") {
      tooltips[i] <- paste0(
        "<div style='max-width:400px;padding:12px;font-family:Arial;'>",
        "<h4 style='color:#2C3E50;'>", htmlEscape(nodes$name[i]), " ", eff_badge, "</h4>",
        "<div style='background:#f8f9fa;padding:8px;border-radius:5px;margin:8px 0;'>",
        "<b>Definition:</b><br>", wrap_text(nodes$Description[i], 60),
        "</div>",
        "<table style='font-size:0.85em;'>",
        "<tr><td><b>Actor:</b></td><td>", htmlEscape(nodes$actor[i]), "</td></tr>",
        "<tr><td><b>Journey:</b></td><td>", htmlEscape(nodes$journey[i]), "</td></tr>",
        "<tr><td><b>COM-B:</b></td><td>", htmlEscape(nodes$comb[i]), "</td></tr>",
        "<tr><td><b>Mentions:</b></td><td>", nodes$mentions[i], "</td></tr>",
        "<tr><td><b>Avg Effect:</b></td><td>", round(nodes$avg_effect[i], 2), 
        " <span style='font-size:0.8em;color:#666;'>(+ = enables, - = blocks)</span></td></tr>",
        "</table></div>"
      )
    } else {
      tooltips[i] <- paste0(
        "<div style='max-width:400px;padding:12px;font-family:Arial;'>",
        "<h4 style='color:#8e44ad;'>", htmlEscape(nodes$name[i]), " (Behavior)</h4>",
        "<div style='background:#f8f9fa;padding:8px;border-radius:5px;'>",
        wrap_text(nodes$Description[i], 60),
        "</div>",
        "<table style='font-size:0.85em;'>",
        "<tr><td><b>Actor:</b></td><td>", htmlEscape(nodes$actor[i]), "</td></tr>",
        "<tr><td><b>Journey:</b></td><td>", htmlEscape(nodes$journey[i]), "</td></tr>",
        "<tr><td><b>Mentions:</b></td><td>", nodes$mentions[i], "</td></tr>",
        "</table></div>"
      )
    }
  }
  return(tooltips)
}

nodes$title <- create_tooltips(nodes)
```

###Identifying gaps that exist in our nodes and edges to guide intervention points
```{r}
# Identify gaps
identify_gaps <- function(nodes_data, edges_data) {
  if(nrow(edges_data) == 0) return(NULL)
  edge_counts <- c(table(edges_data$from), table(edges_data$to))
  node_degrees <- data.frame(
    id = as.numeric(names(edge_counts)),
    degree = as.numeric(edge_counts)
  ) %>% group_by(id) %>% summarise(degree = sum(degree), .groups = "drop")
  
  nodes_data %>%
    left_join(node_degrees, by = "id") %>%
    mutate(
      degree = ifelse(is.na(degree), 0, degree),
      gap_score = mentions / (degree + 1),
      is_gap = gap_score > quantile(gap_score, 0.8, na.rm = TRUE)
    )
}

gap_nodes <- identify_gaps(nodes, edges)
if(!is.null(gap_nodes)) {
  nodes$is_gap <- gap_nodes$is_gap
  cat("\nGaps identified:", sum(nodes$is_gap, na.rm = TRUE), "\n")
}
```

###Adding suggestions from analysis to make map more prescriptive than descriptive and guide ML suggestions later
```{r}
# ============================================
# STAKEHOLDER SUGGESTIONS DATABASE
# ============================================

suggestions_db <- list(
  
  # RECEIVE INFORMATION
  "Receive Information" = list(
    title = "Improving How Citizens Receive Information",
    cross_cutting = "Citizens frame trust reform as both a regulatory problem (misinformation control) and a structural communication problem (weak official channels and civic literacy gaps).",
    
    by_stakeholder = list(
      Citizen = list(
        icon = "👤",
        suggestions = c(
          "Stricter regulation of misinformation - enforce cybercrime laws, penalize false information",
          "Official government communication through verified channels and official handles",
          "Increased civic education and sensitization - educate youth, take engagement to village level",
          "Timely and transparent communication - announce participation early, avoid politicization",
          "Decentralized multi-channel communication - use barazas, radio, social media, print"
        )
      ),
      CSO = list(
        icon = "🏗️",
        suggestions = c(
          "Collaboration across organizations for coordinated messaging",
          "Government should accept citizen voices and create clear trickle-down communication",
          "Professionalization of information handling",
          "Better training of ward administrators"
        ),
        emphasis = "Institutional reform + coordination rather than punishment"
      ),
      `Policy maker` = list(
        icon = "🏛️",
        suggestions = c(
          "Formal online platforms (Twitter spaces, official pages)",
          "Structured dissemination through press conferences and webinars",
          "Controlled communication flows to manage agitation and digital pressure"
        ),
        emphasis = "Formalized, top-down systems with recognition of anger triggers"
      ),
      `Local Govt official` = list(
        icon = "🏘️",
        suggestions = c(
          "Legalize misinformation control mechanisms",
          "Bring engagement closer to village level",
          "Improve procedural adherence and feedback loops"
        ),
        emphasis = "Administrative reform + decentralization"
      ),
      `Religious leader` = list(
        icon = "⛪",
        suggestions = c(
          "Information should come from official organs",
          "Government offices should communicate directly",
          "Extend awareness beyond religious institutions",
          "Face-to-face government-community interface"
        ),
        emphasis = "Authority-linked verification + moral responsibility"
      ),
      `Media professional` = list(
        icon = "📰",
        suggestions = c(
          "Verification before publication",
          "Professional filtering of information",
          "Highlight issues repeatedly to force response",
          "Fact-check before amplifying"
        ),
        emphasis = "Professional gatekeeping"
      ),
      `Social media` = list(
        icon = "📱",
        suggestions = c(
          "Reporting and advocacy increases responsiveness",
          "Trending issues trigger action",
          "Repetition and visibility matter"
        ),
        emphasis = "Visibility power"
      )
    ),
    
    structural_models = c(
      "1. Digital Regulation Model → Legal enforcement to restore trust",
      "2. Official Channel Strengthening → Verified, centralized information sources",
      "3. Civic Literacy Model → Empower citizens through education",
      "4. Decentralization Model → Take communication to ward/village level",
      "5. Transparency & Timeliness → Improve clarity and feedback loops"
    ),
    
    demographic_note = "Youth rely more on digital platforms; older citizens prefer official channels; rural areas emphasize radio and village-level communication; urban areas emphasize online visibility."
  ),
  
  # SHARING INFORMATION
  "Sharing Information" = list(
    title = "Improving How Information Is Shared",
    cross_cutting = "Sharing information is where civic engagement either scales up or breaks down. Three dynamics: Independence + Trust Infrastructure, Reach + Inclusion Architecture, Capacity + Resourcing.",
    
    by_stakeholder = list(
      Citizen = list(
        icon = "👤",
        suggestions = c(
          "Timely, accurate, verified sharing - avoid 'first to share' culture",
          "Local structures for sharing through chiefs, elders, Nyumba-Kumi, barazas",
          "Create/strengthen community group platforms (especially WhatsApp)",
          "Government should communicate directly and publicly",
          "Civic education to enable citizens to share and act correctly"
        )
      ),
      CSO = list(
        icon = "🏗️",
        suggestions = c(
          "Ground-truthing before amplifying - verify by visiting sites",
          "Use structured dissemination tools (newsletters, submissions, forums)",
          "Resource mobilization for dissemination - funds for media and ground reach",
          "Demand transparency and accountability to enable advocacy"
        ),
        emphasis = "Verification + packaging + resourcing"
      ),
      `Policy maker` = list(
        icon = "🏛️",
        suggestions = c(
          "Mobilization through local political brokers",
          "Human-rights based framing for service delivery communication"
        ),
        emphasis = "Pragmatic mobilization tension: turnout vs trust"
      ),
      `Local Govt official` = list(
        icon = "🏘️",
        suggestions = c(
          "Use trusted grassroots relays: Nyumba-Kumi and elders",
          "Institutionalize public health/school-based dissemination",
          "Train local administrators to relay information properly"
        ),
        emphasis = "Channel efficiency + institutional nodes"
      ),
      `Religious leader` = list(
        icon = "⛪",
        suggestions = c(
          "Train communities on rights so they can speak and share confidently",
          "Capacity and resources needed to disseminate",
          "Local representation in leadership improves credibility and reach"
        ),
        emphasis = "Civic literacy + legitimacy"
      ),
      `Media professional` = list(
        icon = "📰",
        suggestions = c(
          "Media independence and neutrality - reduce political capture",
          "Timely civic reporting linked to decision windows",
          "Improve packaging for accessibility (language, simplicity)",
          "Resources and training for journalists",
          "Increase interaction time and community voice in programming"
        ),
        emphasis = "Free, resourced, trained, and interactive media"
      ),
      `Social media` = list(
        icon = "📱",
        suggestions = c(
          "Training and structured platforms for meaningful reporting",
          "Security/protection and clear policy to prevent intimidation",
          "Government should fund/program civic information content"
        ),
        emphasis = "Opportunity + risk: skills, protection, planned content needed"
      )
    )
  ),
  
  # TAKE ACTION
  "Take Action" = list(
    title = "Enabling Citizens to Take Action",
    cross_cutting = "Taking action depends on: lowering cost/friction, converting participation into visible results, and enabling action through capability and authority.",
    
    by_stakeholder = list(
      Citizen = list(
        icon = "👤",
        suggestions = c(
          "Civic education and awareness as the 'spark' for action",
          "Regular, well-designed community meetings with key decision actors",
          "Reduce the 'cost of participation' through transport support and better timing",
          "Fast, visible government response sustains future action",
          "Clear reporting channels and direct contacts for urgent issues",
          "Trust and safety conditions to act without fear or judgment"
        )
      ),
      CSO = list(
        icon = "🏗️",
        suggestions = c(
          "Funding and resourcing to move from concern to action",
          "Stronger government service delivery and 'open door' posture",
          "Legal/institutional enabling environment (PBO Act)",
          "Collective action among CSOs - reduce competition, increase coordination",
          "Capacity building: legal minds, documentation skills, exchange learning",
          "Local resource mobilization as sustainability pathway"
        ),
        emphasis = "Capacity + enabling environment"
      ),
      `Policy maker` = list(
        icon = "🏛️",
        suggestions = c(
          "National mandate and oversight for regional dialogues",
          "Accountability and transparency frameworks",
          "Peer learning among government officials from neighboring wards"
        )
      ),
      `Local Govt official` = list(
        icon = "🏘️",
        suggestions = c(
          "Equip and resource local administrators (vehicles, operational budgets)",
          "Clarify authority and command structures for enforcement",
          "Push resources and decision-making closer to lowest level",
          "Improve government-to-community communication and integrity",
          "Administrative redesign to bring services closer"
        ),
        emphasis = "Operations: tools + budget + clear authority + anti-corruption + proximity"
      ),
      `Religious leader` = list(
        icon = "⛪",
        suggestions = c(
          "Collective responsibility and cooperation for faster solutions",
          "Improve devolution/service decentralization",
          "Civic literacy: help communities make viable demands",
          "Priority-setting by government based on local needs",
          "Action through community participation in solutions (co-production)"
        ),
        emphasis = "Shared responsibility + civic maturity"
      ),
      `Media professional` = list(
        icon = "📰",
        suggestions = c(
          "Media independence as the condition for civic action support",
          "Availability and responsiveness of media as a bridge to action",
          "More interactive programming that converts concern into participation",
          "Training and linkages so reporters can support action effectively"
        ),
        emphasis = "Access + independence + interactivity"
      ),
      `Social media` = list(
        icon = "📱",
        suggestions = c(
          "Independence and transparency about editorial decisions",
          "Reliable access to media actors for rapid action coordination",
          "Government advance notice enables 'action-ready' participation"
        ),
        emphasis = "Speed + clarity + credibility"
      )
    )
  ),
  
  # RESPOND TO CIVIC ACTION
  "Respond to Civic Action" = list(
    title = "Improving Government Response to Civic Action",
    cross_cutting = "Response hinges on four drivers: Speed (timely action), Completion (visible delivery), Transparency (corruption-free processes), and Proximity & Feedback (accessible institutions).",
    
    by_stakeholder = list(
      Citizen = list(
        icon = "👤",
        suggestions = c(
          "Timely and immediate government response as the primary expectation",
          "Visible completion of agreed projects and services",
          "Listening leadership with community involvement in decision-making",
          "Transparency and anti-corruption enforcement",
          "Clear and accessible feedback mechanisms with structured timelines",
          "Proximity of services through genuine devolution",
          "Leadership integrity and accountability"
        )
      ),
      CSO = list(
        icon = "🏗️",
        suggestions = c(
          "Move from policy on paper to implementation in practice",
          "Strengthened feedback and escalation mechanisms",
          "Trust-building through integrity and role clarity",
          "Coordination structures across CSOs",
          "Transparency in public resource allocation"
        ),
        emphasis = "Implementation + coordination challenge"
      ),
      `Policy maker` = list(
        icon = "🏛️",
        suggestions = c(
          "Higher resource allocation at regional and county level",
          "Continuous feedback mechanisms (policies, guidelines, SOPs)",
          "Prioritize realistic, completable commitments",
          "Include implementers in policy formulation",
          "Strengthen constitutional implementation and transparency"
        ),
        emphasis = "Governance design + capacity: realistic planning, fiscal alignment"
      ),
      `Local Govt official` = list(
        icon = "🏘️",
        suggestions = c(
          "Operational capacity: transport, equipment, and mobility",
          "Training and knowledge strengthening for administrators",
          "Funding release and administrative empowerment",
          "Clear jurisdiction and escalation structures"
        ),
        emphasis = "Last-mile administrative constraints"
      ),
      `Religious leader` = list(
        icon = "⛪",
        suggestions = c(
          "Integrate communities in policy-making processes",
          "Raise community participation levels",
          "Respect and implement constitutional provisions"
        ),
        emphasis = "Shared governance responsibility"
      ),
      `Media professional` = list(
        icon = "📰",
        suggestions = c(
          "Sustained follow-up journalism for accountability",
          "Media independence and protection from political interference",
          "Accessible and responsive journalism",
          "Improved regulatory environment for emerging media houses"
        ),
        emphasis = "Accountability monitoring function"
      ),
      `Social media` = list(
        icon = "📱",
        suggestions = c(
          "Freedom of digital expression within safety limits",
          "Expand digital access (e.g., free Wi-Fi)",
          "Reach wider audiences to amplify accountability pressure"
        ),
        emphasis = "Visibility + amplification challenge"
      )
    )
  )
)

# Key insight summary for quick reference
key_insight <- "Civic engagement is not blocked by apathy—it is constrained by information system weaknesses, capacity gaps, and broken feedback loops. Across all journeys, stakeholders demand: verified information, accessible channels, responsive institutions, and genuine inclusion."
```

###UI Definition
```{r}
# ============================================
# UI
# ============================================
ui <- fluidPage(
  theme = shinytheme("flatly"),
  
  tags$head(tags$style(HTML("
    .control-panel { background:#f8f9fa; border-radius:10px; padding:15px; margin-bottom:20px; box-shadow:0 2px 4px rgba(0,0,0,0.1); }
    .stats-card { background:linear-gradient(135deg,#667eea,#764ba2); color:white; border-radius:10px; padding:15px; margin-bottom:15px; text-align:center; }
    .insight-box { background:#f0f8ff; border-left:4px solid #3498db; padding:15px; margin:10px 0; font-family:monospace; white-space:pre-wrap; border-radius:5px; }
    .map-legend { background:white; border:1px solid #ddd; border-radius:8px; padding:12px; margin-top:15px; }
    .legend-item { display:inline-block; margin-right:15px; font-size:12px; }
    .legend-color { display:inline-block; width:12px; height:12px; border-radius:50%; margin-right:5px; }
    .suggestion-card { background:white; border-radius:8px; padding:12px; margin-bottom:10px; box-shadow:0 1px 3px rgba(0,0,0,0.1); }
    .emphasis-box { background:#fef9e7; border-left:4px solid #f39c12; padding:8px 12px; margin-top:8px; border-radius:4px; font-size:0.9em; }
  "))),
  
  titlePanel(
    div(
      h1("🧠 Behavioral Systems Map", style="display:inline-block;margin-right:15px;"),
      span("CSO Decision Support Tool", style="color:#6c757d;font-size:18px;")
    )
  ),
  
  tabsetPanel(
    id = "journey_tabs",
    tabPanel("📥 Receive Information", value = "Receive Information"),
    tabPanel("📤 Share Information", value = "Sharing Information"),
    tabPanel("🎯 Take Action", value = "Take Action"),
    tabPanel("🔄 Respond to Civic Action", value = "Respond to Civic Action"),
    tabPanel("🌐 Full Map", value = "All"),
    tabPanel("💡 Suggestions", value = "suggestions"),
    tabPanel("📖 About COM-B", value = "comb_info")
  ),
  
  br(),
  
  sidebarLayout(
    sidebarPanel(width = 3,
      div(class = "control-panel",
        h4("🎛️ Controls"),
        selectInput("stakeholder", "👥 I am a...",
          choices = c("Civil Society (CSO)"="CSO","Policy Maker"="Policy Maker",
                     "Media"="Media","Local Leader"="Local Leader")),
        hr(),
        h5("🎯 Filters"),
        selectInput("actor", "👤 Actor", choices = c("All", sort(unique(nodes$actor)))),
        selectInput("effect_filter", "📊 Effect Type",
          choices = c("All","Lever (Positive)","Barrier (Negative)","Both/Mixed")),
        selectInput("l3_filter", "📂 System Level (L3)",
  choices = c("All", sort(unique(nodes$l3_category[nodes$l3_category != ""])))),
        checkboxInput("show_gaps", "🔴 Highlight Gaps", FALSE),
        hr(),
        textInput("search", "🔍 Search", placeholder = "Type to search..."),
        hr(),
        # Layout fixed to network view (removed journey steps option temporarily)
        checkboxInput("show_labels", "🏷️ Show Labels", TRUE),
        hr(),
        actionButton("run_ml", "🤖 Generate Insights", class="btn-primary", style="width:100%;"),
        br(), br(),
        downloadButton("download_data", "📥 Download Data", class="btn-info", style="width:100%;")
      )
    ),
    
    mainPanel(width = 9,
      
      # Network Map View
      conditionalPanel("input.journey_tabs == 'Receive Information' || input.journey_tabs == 'Sharing Information' || input.journey_tabs == 'Take Action' || input.journey_tabs == 'Respond to Civic Action' || input.journey_tabs == 'All'",
        visNetworkOutput("network", height = "550px"),
        div(class = "map-legend",
          fluidRow(
            column(4,
              h5("🔵 Nodes"),
              p(span(style="color:#3498db;font-size:18px;","●")," L3 Influence"),
              p(span(style="color:#9b59b6;font-size:18px;","◆")," L2 Behavior"),
              p(span(style="border:3px solid red;padding:2px 8px;border-radius:12px;","⬤")," Gap (high potential)")
            ),
            column(4,
              h5("➡️ Arrows"),
              p(span(style="color:#2ecc71;font-size:18px;","→")," Positive/Lever"),
              p(span(style="color:#e74c3c;font-size:18px;","→")," Negative/Barrier"),
              p(span(style="color:#f39c12;font-size:18px;","→")," Mixed/Neutral")
            ),
            column(4,
              h5("📏 Size = Mentions"),
              p("Larger = More frequent in data")
            )
          )
        )
      ),
      
      # COM-B Info View
      conditionalPanel("input.journey_tabs == 'comb_info'",
  div(style = "max-width:700px; margin:0 auto; padding:20px;",
    div(class = "insight-box",
      h3("📖 What is COM-B?", style = "margin-top:0; font-size:20px;"),
      p("COM-B is a behavioral science framework that helps understand what drives behavior.", 
        style = "font-size:13px; line-height:1.5;"),
      
      fluidRow(
        column(4,
          div(style = "background:#d5f5e3; padding:10px; border-radius:8px; margin-bottom:10px;",
            h4("C", style = "margin:0; color:#27ae60; font-size:16px;"),
            p(strong("Capability"), style = "margin:2px 0; font-size:12px;"),
            p("Knowledge, skills, ability to perform the behavior", style = "font-size:11px; color:#555;")
          )
        ),
        column(4,
          div(style = "background:#d6eaf8; padding:10px; border-radius:8px; margin-bottom:10px;",
            h4("O", style = "margin:0; color:#2980b9; font-size:16px;"),
            p(strong("Opportunity"), style = "margin:2px 0; font-size:12px;"),
            p("Physical and social environment that enables the behavior", style = "font-size:11px; color:#555;")
          )
        ),
        column(4,
          div(style = "background:#fdebd0; padding:10px; border-radius:8px; margin-bottom:10px;",
            h4("M", style = "margin:0; color:#e67e22; font-size:16px;"),
            p(strong("Motivation"), style = "margin:2px 0; font-size:12px;"),
            p("Automatic (emotions/habits) and Reflective (beliefs/intentions)", style = "font-size:11px; color:#555;")
          )
        )
      ),
      
      hr(style = "margin:10px 0;"),
      
      h4("Why We Use COM-B in This Map", style = "font-size:14px;"),
      p("Each influence is tagged with its COM-B component. This helps you identify:", style = "font-size:12px;"),
      tags$ul(style = "font-size:12px;",
        tags$li(strong("Physical Opportunity:"), " Access, infrastructure, resources"),
        tags$li(strong("Social Opportunity:"), " Norms, networks, relationships"),
        tags$li(strong("Psychological Capability:"), " Knowledge, skills, understanding"),
        tags$li(strong("Automatic Motivation:"), " Habits, emotions, impulses"),
        tags$li(strong("Reflective Motivation:"), " Beliefs, values, intentions")
      ),
      
      p(style = "font-size:11px; margin-top:15px;",
        a("🔗 Learn more about COM-B model", 
          href = "https://thedecisionlab.com/reference-guide/organizational-behavior/the-com-b-model-for-behavior-change", 
          target = "_blank")
      )
    )
  )
),
      # Suggestions View
      conditionalPanel("input.journey_tabs == 'suggestions'",
        div(style = "padding: 8px;",
          
          # Key Insight Banner
          div(class = "stats-card",
            h3("💡 Key Insight"),
            p(textOutput("key_insight_text"), style = "font-size:10px;")
          ),
          
          # Current Journey Header
          h3(textOutput("suggestions_title"), style = "color:#2c3e50;"),
          p(em(textOutput("cross_cutting_text")), style = "color:#666;"),
          
          br(),
          
          # Structural Models
          conditionalPanel(
            condition = "output.has_models == true",
            div(class = "insight-box",
              h4("🏗️ Structural Reform Models"),
              uiOutput("structural_models_ui")
            )
          ),
          
          br(),
          
          # Stakeholder-specific suggestions
          h4("👥 Suggestions by Stakeholder"),
          uiOutput("stakeholder_suggestions_ui"),
          
          # Demographic note
          conditionalPanel(
            condition = "output.has_demographics == true",
            br(),
            div(class = "insight-box",
              h4("📊 Demographic Variations"),
              textOutput("demographic_note")
            )
          )
        )
      ),
      
      # Bottom tabs
      tabsetPanel(
        tabPanel("🎯 ML Insights",
          div(class = "stats-card",
            h3(textOutput("insight_title")),
            p("Strategic Analysis Based on Current View")
          ),
          div(class = "insight-box", style = "font-size:12px; max-height:300px; overflow-y:auto;",
  verbatimTextOutput("ml_insights")
)
        ),
        tabPanel("📊 Data Table", DTOutput("data_table", height = "200px")),
        tabPanel("📖 Glossary", DTOutput("glossary_table", height = "200px"))
      )
    )
  )
)
```

###Server Function Definition
```{r}
# ============================================
# SERVER
# ============================================
server <- function(input, output, session) {
  
  # Update filters based on tab selection
  observeEvent(input$journey_tabs, {
    if(input$journey_tabs != "All" && input$journey_tabs != "comb_info" && input$journey_tabs != "suggestions") {
      updateSelectInput(session, "actor", selected = "All")
    }
  })
  
  # Reactive filtering
  filtered_nodes <- reactive({
    df <- nodes
    
    # Journey filtering - check exact values in data
if(input$journey_tabs != "All" && input$journey_tabs != "comb_info" && input$journey_tabs != "suggestions") {
  cat("\nFiltering journey:", input$journey_tabs, "\n")
  cat("Unique journeys in data:", paste(unique(df$journey), collapse = ", "), "\n")
  df <- df %>% filter(journey == input$journey_tabs)
  cat("Rows after journey filter:", nrow(df), "\n")
}
    
    if(!is.null(input$actor) && input$actor != "All") {
      df <- df %>% filter(actor == input$actor)
    }
    
    if(!is.null(input$effect_filter) && input$effect_filter != "All") {
      df <- df %>% filter(effect_type == input$effect_filter)
    }
    
    if(!is.null(input$search) && input$search != "") {
      df <- df %>% filter(str_detect(tolower(name), tolower(input$search)))
    }
    
    if(input$show_gaps && !is.null(nodes$is_gap)) {
  df$color.border <- ifelse(df$is_gap, "#ff0000", "#333333")
  df$borderWidth <- ifelse(df$is_gap, 4, 1)
}
    if(!is.null(input$l3_filter) && input$l3_filter != "All") {
  df <- df %>% filter(l3_category == input$l3_filter)
  }
    
    df
  })
  
  filtered_edges <- reactive({
    valid_ids <- filtered_nodes()$id
    edges %>% filter(from %in% valid_ids & to %in% valid_ids)
  })
  
  # Network visualization
    # Network visualization
  output$network <- renderVisNetwork({
    req(nrow(filtered_nodes()) > 0)
    vis_nodes <- filtered_nodes() %>% mutate(label = if(input$show_labels) name else "")
    
    visNetwork(vis_nodes, filtered_edges()) %>%
      visEdges(
        arrows = list(to = list(enabled = TRUE, scaleFactor = 0.6)),
        smooth = list(enabled = TRUE, type = "continuous"),
        color = list(inherit = TRUE),
        length = 250
      ) %>%
      visNodes(
        shadow = list(enabled = TRUE, size = 3), 
        font = list(size = 11),
        scaling = list(min = 15, max = 35)
      ) %>%
      visOptions(
        highlightNearest = list(enabled = TRUE, degree = 2, hover = TRUE),
        nodesIdSelection = TRUE
      ) %>%
      visInteraction(hover = TRUE, tooltipDelay = 0, navigationButtons = TRUE) %>%
      visPhysics(
        solver = "forceAtlas2Based",
        stabilization = list(enabled = TRUE, iterations = 1000),
        forceAtlas2Based = list(
          gravitationalConstant = -50,
          centralGravity = 0.01,
          springLength = 200,
          springConstant = 0.08
        )
      )
  })
  
  # ============================================
  # SUGGESTIONS SERVER LOGIC
  # ============================================
  
  # Reactive suggestion data
  current_suggestions <- reactive({
    # Get the active journey from the main tabs, or default
    active_journey <- input$journey_tabs
    if(active_journey %in% names(suggestions_db)) {
      suggestions_db[[active_journey]]
    } else {
      suggestions_db[["Receive Information"]]
    }
  })
  
  output$key_insight_text <- renderText({ key_insight })
  
  output$suggestions_title <- renderText({
    req(current_suggestions())
    current_suggestions()$title
  })
  
  output$cross_cutting_text <- renderText({
    req(current_suggestions())
    current_suggestions()$cross_cutting
  })
  
  output$has_models <- reactive({
    req(current_suggestions())
    !is.null(current_suggestions()$structural_models)
  })
  outputOptions(output, "has_models", suspendWhenHidden = FALSE)
  
  output$has_demographics <- reactive({
    req(current_suggestions())
    !is.null(current_suggestions()$demographic_note)
  })
  outputOptions(output, "has_demographics", suspendWhenHidden = FALSE)
  
  output$structural_models_ui <- renderUI({
    req(current_suggestions())
    models <- current_suggestions()$structural_models
    
    tagList(
      lapply(models, function(m) {
        p(m, style = "margin:5px 0;")
      })
    )
  })
  
  output$demographic_note <- renderText({
    req(current_suggestions())
    current_suggestions()$demographic_note
  })
  
  output$stakeholder_suggestions_ui <- renderUI({
    req(current_suggestions())
    stakeholders <- current_suggestions()$by_stakeholder
    
    panels <- lapply(names(stakeholders), function(stake_name) {
      stake <- stakeholders[[stake_name]]
      
      div(class = "suggestion-card",
        h5(paste(stake$icon, stake_name), style = "margin-top:0;"),
        tags$ul(style = "margin-bottom:5px;",
          lapply(stake$suggestions, function(s) {
            tags$li(s, style = "font-size:0.9em; margin-bottom:3px;")
          })
        ),
        if(!is.null(stake$emphasis)) {
          div(class = "emphasis-box",
            strong("🎯 Emphasis: "), stake$emphasis
          )
        }
      )
    })
    
    do.call(tagList, panels)
  })
  
  # ============================================
  # ML INSIGHTS (UPDATED WITH SUGGESTIONS)
  # ============================================
  
  ml_results <- reactiveVal("Click 'Generate ML Insights' to analyze the network.\n\nNavigate to the 💡 Suggestions tab for stakeholder recommendations.")
  
  observeEvent(input$run_ml, {
  current_journey <- input$journey_tabs
  
  # Get filtered data
  f_nodes <- filtered_nodes()
  f_edges <- filtered_edges()
  
  # Separate influences and behaviors
  inf_nodes <- f_nodes %>% filter(type == "Influence")
  beh_nodes <- f_nodes %>% filter(type == "Behavior")
  
  # Count effects
  n_levers <- sum(inf_nodes$effect_type == "Lever (Positive)")
  n_barriers <- sum(inf_nodes$effect_type == "Barrier (Negative)")
  n_mixed <- sum(inf_nodes$effect_type == "Both/Mixed")
  
  # Top barriers (negative effect influences)
  top_barriers <- inf_nodes %>%
    filter(effect_type == "Barrier (Negative)") %>%
    arrange(desc(mentions)) %>%
    head(5) %>%
    pull(name)
  
  # Top levers (positive effect influences)
  top_levers <- inf_nodes %>%
    filter(effect_type == "Lever (Positive)") %>%
    arrange(desc(mentions)) %>%
    head(5) %>%
    pull(name)
  
  # Most connected nodes (centrality)
  edge_counts <- c(table(f_edges$from), table(f_edges$to))
  if(length(edge_counts) > 0) {
    node_connections <- data.frame(
      id = as.numeric(names(edge_counts)),
      connections = as.numeric(edge_counts)
    ) %>%
      group_by(id) %>%
      summarise(connections = sum(connections), .groups = "drop")
    
    central_nodes <- f_nodes %>%
      left_join(node_connections, by = "id") %>%
      mutate(connections = ifelse(is.na(connections), 0, connections)) %>%
      filter(type == "Influence") %>%
      arrange(desc(connections)) %>%
      head(5)
  } else {
    central_nodes <- data.frame(name = "N/A", connections = 0)
  }
  
  # Gaps
  gap_count <- sum(f_nodes$is_gap, na.rm = TRUE)
  gap_names <- f_nodes %>%
    filter(is_gap) %>%
    arrange(desc(mentions)) %>%
    head(5) %>%
    pull(name)
  
  # Build insights
  insights <- paste0(
    "╔══════════════════════════════════════╗\n",
    "║   📊 STRATEGIC ANALYSIS              ║\n",
    "║   Stakeholder: ", sprintf("%-22s", input$stakeholder), "║\n",
    "╚══════════════════════════════════════╝\n\n",
    
    "📈 NETWORK OVERVIEW\n",
    "─────────────────────────────────────────\n",
    "   • Total Nodes: ", nrow(f_nodes), 
    " (", nrow(inf_nodes), " influences, ", nrow(beh_nodes), " behaviors)\n",
    "   • Connections: ", nrow(f_edges), "\n",
    "   • Density: ", ifelse(nrow(f_nodes) > 1, 
        round(nrow(f_edges) / (nrow(f_nodes) * (nrow(f_nodes) - 1)), 3), 0), "\n\n",
    
    "🔴 TOP BARRIERS (What Blocks Action)\n",
    "─────────────────────────────────────────\n",
    if(length(top_barriers) > 0) {
      paste0("   ", 1:length(top_barriers), ". ", top_barriers, 
             " (Mentions: ", inf_nodes$mentions[match(top_barriers, inf_nodes$name)], ")\n", collapse = "")
    } else {
      "   No strong barriers identified in current view.\n"
    }, "\n",
    
    "🟢 TOP LEVERS (What Enables Action)\n",
    "─────────────────────────────────────────\n",
    if(length(top_levers) > 0) {
      paste0("   ", 1:length(top_levers), ". ", top_levers,
             " (Mentions: ", inf_nodes$mentions[match(top_levers, inf_nodes$name)], ")\n", collapse = "")
    } else {
      "   No strong levers identified in current view.\n"
    }, "\n",
    
    "🎯 CENTRAL NODES (Most Connected)\n",
    "─────────────────────────────────────────\n",
    if(nrow(central_nodes) > 0) {
      paste0("   ", 1:nrow(central_nodes), ". ", central_nodes$name,
             " (", central_nodes$connections, " connections)\n", collapse = "")
    } else {
      "   No connections in current view.\n"
    }, "\n",
    
    "🔴 GAPS (High Potential, Low Connections)\n",
    "─────────────────────────────────────────\n",
    if(gap_count > 0) {
      paste0("   Found: ", gap_count, " gaps\n",
             paste0("   • ", head(gap_names, 5), "\n", collapse = ""))
    } else {
      "   No gaps identified. Enable 'Highlight Gaps' to detect.\n"
    }
  )
  
  # Add stakeholder-specific suggestions
  suggestions_text <- ""
  if(current_journey %in% names(suggestions_db)) {
    journey_sug <- suggestions_db[[current_journey]]
    stake_key <- input$stakeholder
    
    stake_mapping <- c(
      "CSO" = "CSO",
      "Policy Maker" = "Policy maker",
      "Media" = "Media professional",
      "Local Leader" = "Local Govt official"
    )
    
    mapped_key <- stake_mapping[stake_key]
    if(is.null(mapped_key)) mapped_key <- "Citizen"
    
    stake_sug <- journey_sug$by_stakeholder[[mapped_key]]
    
    if(!is.null(stake_sug)) {
      suggestions_text <- paste0(
        "\n\n💡 RECOMMENDATIONS FOR ", toupper(stake_key), "\n",
        "─────────────────────────────────────────\n",
        "Based on stakeholder data for '", current_journey, "':\n\n",
        paste0("   ✅ ", stake_sug$suggestions, collapse = "\n"),
        if(!is.null(stake_sug$emphasis)) {
          paste0("\n\n   🎯 PRIORITY: ", stake_sug$emphasis)
        } else ""
      )
    }
  }
  
  ml_results(paste0(insights, suggestions_text))
})
  
  output$ml_insights <- renderText({ ml_results() })
  output$insight_title <- renderText({ paste(input$stakeholder, "Strategic Analysis") })
  
  # Data table
  output$data_table <- renderDT({
    datatable(
      filtered_nodes() %>% filter(type == "Influence") %>%
        select(Name = name, Actor = actor, Journey = journey, Mentions = mentions, Effect = effect_type),
      options = list(pageLength = 10, dom = 'Bt'), rownames = FALSE
    ) %>% formatStyle('Effect', backgroundColor = styleEqual(
      c("Lever (Positive)","Barrier (Negative)","Both/Mixed"),
      c("#d4edda","#f8d7da","#fff3cd")))
  })
  
  # Glossary table
  output$glossary_table <- renderDT({
    datatable(
      glossary_clean %>% select(Term = name, Definition = definition, Level = level),
      options = list(pageLength = 15, dom = 'Bt'), rownames = FALSE
    ) %>% formatStyle('Level', backgroundColor = styleEqual(
      c("L4 System Level"), c("#fdebd0"))) %>%
      formatStyle('Term', fontWeight = styleEqual(
        glossary_clean$name[glossary_clean$is_l4], rep("bold", sum(glossary_clean$is_l4))))
  })
  
  # Download handler
  output$download_data <- downloadHandler(
    filename = function() paste0("behavioral_data_", Sys.Date(), ".csv"),
    content = function(file) write.csv(filtered_nodes(), file, row.names = FALSE)
  )
}
```

###Running Application
```{r}
# Run the application
shinyApp(ui = ui, server = server)
```

